---
title: "Example: Other Packages"
output: rmarkdown::html_vignette
resource_files:
  - fig2.png
vignette: >
  %\VignetteIndexEntry{Example: Other Packages}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rsppfp)
library(igraph)
library(foreach)
library(doParallel)
library(dplyr)
```


This is an example to showcase how **rsppfp** can be used along with other existing packages. 


## Preparing the Input

The first step is to define the graph and its forbidden paths. This is done in the following snippet, with a set of forbidden paths defined as `F = {f_1, f_2, f_3, f_4}`, where `f_1 = {u, v, y, u}`, `f_2 = {w, u, y, u}`, `f_3 = {w, v, y}` and `f_4 = {x, w, v, y, t}`. Though this example is defined arbitrarily, and the input data is hard-coded, it is worth noting that the input can be obtained from different sources such as databases, spreadsheet files, and others. However, that process is outside of **rsppfp**’s scope. 


```{r}
# Load the sample graph
graph <- data.frame(from = c("s", "s", "s", "u", "u", "w", "w", "x", "x", "v", "v", "y", "y"),
                    to = c("u", "w", "x", "w", "v", "v", "y", "w", "y", "y", "t", "t", "u"),
                    cost = c(1L, 4L, 1L, 2L, 7L, 1L, 2L, 5L, 1L, 4L, 1L, 3L, 9L),
                    stringsAsFactors = FALSE)

# Load the forbidden paths
fpaths <- data.frame(V1 = c("u", "u", "w", "x"), V2 = c("v", "w", "v","w"), V3 = c("y", "y", "y", "v"),
                     V4 = c("u", "u", NA, "y"), V5 = c(NA, NA, NA, "t"), stringsAsFactors = FALSE)
```


After this, it is possible to use **rsppfp**’s functions to transform the original graph, into `G*`. In this case, some forbidden paths have sub-paths that are part of others; particular examples are `f_3` and `f_4`. As a result, the example makes use of Hsu’s backward construction function. 

```{r}
# Run the algorithm and transform the graph
gStar <- modify_graph_hsu(graph, fpaths)
gStar
```



## Integration with igraph

The resulting data frame  (named in the code as `gStar`) can be transformed to other data types, specific of particular libraries. For example, it is possible to use the function `graph_from_data_frame(...)` provided by igraph (Csárdi & Nepusz, 2006), to convert `gStar` in order to use iGraph shortest-path functionalities.


```{r}
# Transform gStar to igraph's data format
gStar.igraph <- graph_from_data_frame(gStar)
```

Even more, both graphs can be plotted using `tkplot(…)` or `plot(...)` function. The following code shows an example of visualization using igraphs functions.

```{r, fig.show='hold'}
# This can be used to plot the graph
plot(gStar.igraph, edge.arrow.size = 0.5, vertex.size = 20, xlab = "Graph", 
     vertex.color = "#F1F1F1", vertex.label.color = "#050505")
```

As any path calculated in `gStar` will be given in terms of its nodes. Hence, as a result of the transformation process, `gStar` nodes `nStar` are equivalences of the original nodes. For example, a node labeled `Argo123` in the original graph `G` can be divided into several new `nStar_i`, resulting in: `Troya789|Argo123`, `Paris456|Troya789|Argo123` and `Polux852|Argo123`, besides the original node. Therefore, when searching for a path from a node to another node `n_i`, the algorithm must consider all of the `nStar_i`.

The package **rsppfp** provides an additional function to obtain this equivalences. A code example can be seen below:

```{r}
# This can be used to plot the graph
get_all_nodes(gStar, "v")
```

With this, the flow to obtain a _shortest path_ with any algorithm, can be summarized as follows:
  1. Obtain all of the target node's equivalences.
  2. For each target node found in (1):
    - Get the shortest path and its weight/cost from the origin node to it.
  3. The less costly path is the solution.

This algorithm has been implemented for igraph in an example function, named [`get_shortest_path`](reference/get_shortest_path.html). However, although it can be used to simplify solving the shortest path, its aim is to provide guidance on how to impliment the previous logic.

Its code is the following:

```{r, eval=FALSE}
get_shortest_path <- function(g, origin, dest, weightColName) {
  #If there is no weight column
  if(!weightColName %in% colnames(g)) {
    g$weight <- 1
    weightColName <- "weight"
  }
  
  # Convert the graph
  g.i <- graph_from_data_frame(g)
  
  
  # Get all nodes where for the destination is the destination
  destEq <- get_all_nodes(gStar, dest)
  
  # Find shortest paths from "s" to all N* corresponding to "w"
  sp <- shortest_paths(gStar.igraph, from = origin, to = destEq, 
                       weights = gStar$weightColName, output = "both")
  
  
  # Find shortest of these paths
  dist <- vapply(sp$epath, function(path) sum(path$weightColName), numeric(1)) 
  shortestPath <- sp$vpath[[which.min(dist)]]

  # Convert path with nodes from N* to path with nodes from N
  return( parse_vpath(names(shortestPath)) )
}
```

And it can be used as in the following example:

```{r, warning=FALSE}
# Obtain the shortest path using the simplified function
shortestPath <- get_shortest_path(gStar, "u", "t", "cost")
shortestPath
```

Also, it is worth pointing out that a path can only be translated if it is presented as a list or vector of nodes, written sequentially. In igraph, this is known as `vpaths` (vertexes paths). However, this step is done inside the convenience function.
