---
title: "Example: Other Packages"
output: rmarkdown::html_vignette
resource_files:
  - fig2.png
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(rsppfp)
library(igraph)
library(foreach)
library(doParallel)
library(dplyr)
library(magrittr)
```


This is an example to showcase how **R-SPPFP** can be used along with other existing packages. The full code is accessible from R-SPPFP’s GitHub repository in the [examples package](https://github.com/melvidoni/rsppfp/tree/master/examples). 


## Preparing the Input

The first step is to define the graph and its forbidden paths. This is done in the following snippet, with a set of forbidden paths defined as `F = {f_1, f_2, f_3, f_4}`, where `f_1 = {u, v, y, u}`, `f_2 = {w, u, y, u}`, `f_3 = {w, v, y}` and `f_4 = {x, w, v, y, t}`. Though this example is defined arbitrarily, and the input data is hard-coded, it is worth noting that the input can be obtained from different sources such as databases, spreadsheet files, and others. However, that process is outside of **R-SPPFP**’s scope. 


```{r}
# Load the sample graph
graph <- structure(list(from = c("s", "s", "s", "u", "u", "w", "w", "x", "x", "v", "v", "y", "y"),
                        to = c("u", "w", "x", "w", "v", "v", "y", "w", "y", "y", "t", "t", "u"),
                        cost = c(1L, 4L, 1L, 2L, 7L, 1L, 2L, 5L, 1L, 4L, 1L, 3L, 9L)),
                   .Names = c("from", "to", "cost"), class = "data.frame", row.names = c(NA, -13L))

# Load the forbidden paths
fpaths <- structure(list(V1 = c("u", "u", "w", "x"), V2 = c("v", "w", "v","w"), V3 = c("y", "y", "y", "v"),
                         V4 = c("u", "u", "", "y"), V5 = c("", "", "", "t")),
                    .Names = c("V1", "V2", "V3", "V4", "V5"), class = "data.frame", row.names = c(NA, -4L))
```


After this, it is possible to use **R-SPPFP**’s functions to transform the original graph, into `G*`. In this case, some forbidden paths have sub-paths that are part of others; particular examples are `f_3` and `f_4`. As a result, the example makes use of Hsu’s backward construction function. 

```{r}
# Run the algorithm and transform the graph
gStar <- modify_graph_hsu(graph, fpaths, 3L)
gStar
```



## Integration with iGraph

The resulting data frame  (named in the code as `gStar`) can be transformed to other data types, specific of particular libraries. For example, it is possible to use the function `graph_from_data_frame(...)` provided by iGraph (Csárdi & Nepusz, 2006), to convert `gStar` in order to use iGraph shortest-path functionalities.


```{r}
# Transform gStar to iGraph's data format
gStar.igraph <- graph_from_data_frame(gStar)
```

Even more, both graphs can be plotted using `tkplot(…)` or `plot(...)` function. The following code shows an example of visualization using iGraphs functions.

```{r, fig.show='hold'}
# This can be used to plot the graph
plot(gStar.igraph, edge.arrow.size = 0.5, vertex.size = 20, xlab = "Graph", vertex.color = "#F1F1F1", vertex.label.color = "#050505")
```

As any path calculated in `gStar` will be given in terms of its nodes, it is required to translate it back to the original graph's nodes. The  following code shows that you can use iGraph's `shortest_paths(...)` functions, and then parse the result. This also works with any other path generator function.

It is worth pointing out that a path can only be translated if it is presented as a list or vector of nodes, written sequentially. In iGraph, this is known as `vpaths` (vertexes paths).

```{r}
# Obtain a shortest path
shortestPath <- V(gStar.igraph)$name[ shortest_paths(gStar.igraph, from = "u", to = "t", mode = "out", output = "vpath")$vpath[[1]] ]
shortestPath

# Translate the vpath
parse_vpath(shortestPath)
```






